Velocity Map Imaging Spectroscopy of C$_2$H$^-$ and C$_2$D$^-$: a benchmark study of vibronic coupling interactions

### 2022-06-24 Resubmission/ResponseLetter.tex

We have included statements on page 14 to highlight these points, including: `Photodetachment at 266~nm (4.66~eV) maps out more of the $\tilde{A} ^2\Pi$ potential energy surface, at the cost of lower electron velocity resolution.' $\dots$ `By showing the convolved spectrum, the suitability of the QVC model to simulate spectra capable of direct comparison to experimental or astronomical data can be examined.' 
\vspace*{-2ex}
\begin{verbatim}
----------------------------------------------------------------------
Reviewer #3  
----------------------------------------------------------------------
\end{verbatim}
\vspace*{-2ex}
\emph{This work presents a study of C2H and C2D via photodetachment of the associated anions. These are important astophysical species but represent a spectroscopic challenge with their attendant Herzberg-Teller coupling making simple harmonic assignment impractical. The interaction between the neutral sigma and pi states also represents a challenge for theory and therefore full understanding of spectra.
	The authors present a very nice, combined theoretical and experimental study which (in addition to everything else) represents how science is supposed to work. The spectra are well presented, at good resolution (for photoelectron spectroscopy) and the simulations (at a high level of theory) nicely explain/highlight the effect of the HT coupling. The work is supported by an analysis of the photoelectron angular distributions associated with each transition, vindicating the spectral assignments.
	Overall this is a very nice piece of work which will be an important contribution - it should be published as is (and forthwith)}

We thank Reviewer \#3 for their comments.

\vspace*{-2ex}\ \\ 
\textbf{Statement}\\[.5ex]
This manuscript is not being considered by any other journal.

%\closing{Regards,\\
\   
\includegraphics[width=.2\textwidth,clip]{signatureXX}
               \closing{Regards,}
\end{letter}
\end{sf}
\end{document}
